% 18 Jan 25
%-----------------------------------------------------------------------------
\def\tildetext{\char`\~{}}
\def\tildett{{\tt\tildetext}}
\font\titlefont=cmbx10 scaled \magstep2
%-----------------------------------------------------------------------------
\magnification=\magstep1
\tolerance=16000
\baselineskip 11pt
\nopagenumbers
% \pageno=1
\footline={\hss\tenrm\folio\hss}
%-----------------------------------------------------------------------------

\centerline{\titlefont CHRISTOPHER M. CORNWELL}

% \smallskip
%
% \centerline {\bf CURRICULUM VITAE}

\smallskip
\hrule

\bigskip
\bigskip

\noindent {\bf CONTACT}

\bigskip

\itemitem{} John Munro Godfrey, Sr. Department of Economics
\itemitem{} Terry College of Business
\itemitem{} University of Georgia
\itemitem{} Athens GA 30602

\smallskip

\itemitem{} +1 706 248 0971

\smallskip

\itemitem{} {\tt cornwl@uga.edu}
\itemitem{} {\tt cornwl.github.io}

\bigskip

\noindent {\bf EDUCATION}

\bigskip

\itemitem{} PhD, Michigan State University, 1985
\itemitem{} Major Fields: Econometrics, Labor Economics
% \itemitem{} Dissertation Title:
%       {\it Panel Data with Cross-Section Variation in Slopes and Intercepts}
% \itemitem{} Dissertation Chairperson: Peter Schmidt

\medskip

\itemitem{} BA, Summa Cum Laude,
            University of North Carolina at Chapel Hill, 1981
\itemitem{} Major: Economics

\bigskip

\noindent {\bf POSITIONS HELD}

\bigskip

\item{} {\bf Current}

\bigskip

\itemitem{}
November 2024--Present: Director, M. Douglas and V. Kay Ivester InstituteJoh for Business Analytics and Insights,
Terry College of Business, University of Georgia

\medskip

\itemitem{}
September 2018--Present: Simon S. Selig Jr. Chair for Economic Growth,
Department of Economics, University of Georgia

\medskip

\itemitem{}
September 2002--Present: Professor,
Department of Economics, University of Georgia

\medskip

\itemitem{}
September 2008--Present: Adjunct Professor,
Department of Public Administration and Policy, University of Georgia

\medskip

\itemitem{}
January 2004--Present: Senior Fellow,
Institute of Higher Education, University of Georgia

\bigskip

\item{} {\bf Past}

\bigskip

\itemitem{}
September 2023--November 2024: Director, Center for Business Analytics and Insights,
Terry College of Business, University of Georgia

\itemitem{}
July 2008--June 2023: Head, Department of Economics, University of Georgia

\medskip

\itemitem{}
May 2004--June 2008: Director, Leonard Leadership Scholars Program,
Institute for Leadership Advancement, Terry College of Business

\medskip

\itemitem{}
May 2005--June 2006: Interim Director, Institute for Leadership
Advancement, Terry College of Business

\medskip

\itemitem{}
September 2002--May 2005: Graduate Coordinator, Department of
Economics, University of Georgia

\medskip

\itemitem{}
May 2002, 2003, 2004: Visiting Professor,
Department of Economics, Central European University, Budapest, Hungary

\medskip

\itemitem{}
September 1994--August 2002: Associate Professor,
Department of Economics, University of Georgia

\medskip

\itemitem{}
September 1997--April 1998: Visiting Scholar,
Federal Reserve Bank of Cleveland

\medskip

\itemitem{}
November 1996: Visiting Lecturer,
Institut d'Administration des Enterprises,
Universit\'e Jean Moulin--Lyon 3, Lyon, France

\medskip

\itemitem{}
October 1995: Visiting Lecturer,
Department of Econometrics, Monash University, Melbourne, Australia

\medskip

\itemitem{}
June 1994--July 1994: Visiting Associate Professor,
Lehrstuhl f\"ur Statistik und \"Okonometrie,
Universit\"at Erlangen--N\"urnberg, N\"urnberg, Germany

\medskip

\itemitem{}
September 1988--August 1994: Assistant Professor,
Department of Economics, University of Georgia

\medskip

\itemitem{}
August 1985--August 1988: Assistant Professor,
Department of Economics, West Virginia University

% \medskip
%
% \itemitem{}
% September 1981--July 1985: Graduate Assistant,
% Department of Economics, Michigan State University

\bigskip

\noindent {\bf COURSES TAUGHT}

\bigskip

\item{} {\bf Undergraduate}

\bigskip

\itemitem{} Data Science for Business and Economics
\itemitem{} Introductory Econometrics
\itemitem{} Labor Economics
\itemitem{} Economics of Human Resources
\itemitem{} Intermediate Micro Theory
\itemitem{} Micro Principles (regular and honors sections)

\bigskip

\item{} {\bf PhD}

\bigskip

\itemitem{} Introductory Econometrics (core)
\itemitem{} Econometrics I (field)

\bigskip

\item{} {\bf MSBA}

\bigskip

\itemitem{} Causal Inference

\bigskip

\item{} {\bf MBA}

\bigskip

\itemitem{} Economic Analysis for Business Leaders
\itemitem{} Economics of Managing Organizations

\vfil\eject

\noindent {\bf HONORS AND AWARDS}

\bigskip

\itemitem{}
Selected for inclusion in the 4th edition of {\it Who's Who in Economics\/}
(Edward Elgar, 2003) as one of the 1,200 most frequently cited economists
in the years 1990-2000 using the Social Science Citation Index

\medskip

\itemitem{} Department of Economics' Swift Award for Outstanding Undergraduate Teaching, 2002 and 2009

\medskip

\itemitem{} Student Government Outstanding Teacher Award, 2000

\medskip

\itemitem{} Lothar Tresp Honors Professor, 1999

\medskip

\itemitem{} Terry/Selig Fellow, Terry College of Business, UGA, 1991--97

\medskip

\itemitem{} Kamerschen-Hampton Research Award, Department of Economics,
            UGA, 1994 and 2013

\medskip

\itemitem{} Sarah Moss Fellowship, UGA, 1994

\bigskip

\noindent {\bf GRANTS}

\bigskip

\item{} {\bf External}

\bigskip

\itemitem{} National Science Foundation Grant, PI, \$176,080, 2002--2004

\medskip

\itemitem{} American Education Research Association, Co-PI, \$25,000, 2002--2003

\medskip

\itemitem{} National Science Foundation Grant, PI, \$124,959, 2000--2002

\medskip

\itemitem{} US Department of Labor/PWBA Grant, PI, \$14,400, 1996

\medskip

\itemitem{} W.~E.~Upjohn Institute for Employment Research Grant, \$33,997, Co-PI, 1994

\bigskip

\item{} {\bf Internal}

\bigskip

\itemitem{} Terry-Sanford Research Grant, 1999--2008

\medskip

\itemitem{} University of Georgia Research Foundation Grant, 1989, 1990

\bigskip

\noindent {\bf PUBLICATIONS} % ($^*$indicates publications in the last 3 years)

\bigskip

\item{} {\bf Books}

\bigskip

% \itemitem{*}
\itemitem{}
{\it Pensions and Productivity\/}
(with S. Dorsey and D. Macpherson),
Kalamazoo: Upjohn Institute (1998).

\bigskip

\item{} {\bf Refereed Papers}  %(* indicates accepted for publication in the last 3 years)

\bigskip

\medskip

\itemitem{}
``The Power of Lakshmi: Monetary Incentives for Raising a Girl''
(with N. Biswas and L. Zimmermann), {\it Journal of Human Resources\/}, forthcoming.

\medskip

\itemitem{}
``Building a Productive Workforce: The Role of Structured Management Practices''
(with I. Schmutte and D. Scur), {\it Management Science\/} 67 (2021) 7291-7950.
%{\bf [Accepted 2020]}

\medskip

\itemitem{}
``Wage Discrimination when Identity is Subjective: Evidence from Changes in Employer-Reported Race''
(with J. Rivera and I. Schmutte), {\it Journal of Human Resources\/} 52 (2017) 719-755.

\medskip

\itemitem{}
``Effects of the BAPCPA on the Chapter Composition of Consumer Bankruptcies''
(with B. Xu), {\it Economics Letters\/} 124 (2014) 439-442.
%{\bf [Accepted 2014]}

\medskip

\itemitem{}
``Inference in Two-Step Panel Data Models with Time-Invariant Regressors:
Bootstrap versus Analytical Procedures'' (with S. Atkinson)
in R.~C.~Sickles and W.~C.~Horrace eds.,
{\it Festschrift in Honor of Peter Schmidt},
New York: Springer (2014).
%{\bf [Accepted 2014]}

\medskip

\itemitem{}
``The Long-run Effect of Abortion on Sexually Transmitted Infections''
(with S. Cunningham), {\it American Law and Economics Review\/} 15 (2013) 381-407.

\medskip

\itemitem{}
``Non-cognitive Skills and Gender Disparities in Test Scores and Teacher Assessments:
Evidence from Primary School''
(with D. Mustard and J. Van Parys), {\it Journal of Human Resources\/} 48 (2013) 236-264.

\medskip

\itemitem{}
``Estimation of Allocative Efficiency and Productivity Growth with Dynamic
  Adjustment Costs''
(with S. Atkinson), {\it Econometric Reviews\/} 30 (2011) 337-357.

\medskip
\itemitem{}
``A Pseudo-Sequential Choice Model for Valuing Multiple Environmental Policy and
  Program Components in Contingent Valuation Applications''
(with J. Bergstrom, T. Holmes and D. Volinskiy),
{\it Agricultural and Resource Economics Review\/} 39 (2010) 9-21.

\medskip

\itemitem{}
``Stochastic Frontier Analysis and Panel Data''
(with P.~Schmidt)
in L.~M\'aty\'as and P.~Sevestre eds.,
{\it The Econometrics of Panel Data\/} vol 3,
Dordrecht: Kluwer Academic Publishers (2008).

\medskip

\itemitem{}
``Merit-Based College Scholarships and Car Sales''
(with D. Mustard),
{\it Education Finance and Policy\/} 2 (2007) 133-151.

\medskip

\itemitem{}
``The Enrollment Effects of Merit-Based Financial Aid: Evidence
from Georgia's
  HOPE Scholarship''
(with D. Mustard and D. Sridhar),
{\it Journal of Labor Economics\/} 24 (2006) 761-786.

\medskip

\itemitem{}
``Student Responses to Merit Scholarship Retention Rules''
(with K. Lee and D. Mustard),
{\it Journal of Human Resources\/} 40 (2005) 895-917.

\medskip

\itemitem{}
``Measuring Productivity Change Using a Malmquist Index: Stochastic
  Distance Function Estimation vs DEA''
(with S.~Atkinson and O. Honerkamp),
{\it Journal of Business and Economic Statistics\/} 21 (2003) 284-295.

\medskip

% \itemitem{*}
\itemitem{}
``Survey Response-Related Biases in Contingent Valuation:
  Concepts, Remedies and Empirical Application''
(with M. Messonnier, J. Bergstrom, R. Teasley, and H. Cordell)
{\it American Journal of Agricultural Economics\/} 82 (2000) 438--451.

\medskip

% \itemitem{*}
\itemitem{}
``Estimating Radial Measures of Productivity Growth:
  Frontier vs Non-Frontier Approaches''
(with S.~Atkinson)
{\it Journal of Productivity Analysis\/} 10 (1998) 35--46.

\medskip

% \itemitem{*}
\itemitem{}
``Using Profit and Cost Frontiers to Estimate Price and Technical
  Inefficiency:  A Parametric Approach with Panel Data''
(with S.~Atkinson)
{\it Southern Economic Journal\/} 64 (1998) 753--764.

\medskip

% \itemitem{*}
\itemitem{}
``Unobservable Individual Effects, Marital Status
  and the Earnings of Young Men''
(with P.~Rupert),
{\it Economic Inquiry\/} 35 (1997) 285--294.

\medskip

% \itemitem{*}
\itemitem{}
``Production Frontiers and Efficiency Measurement''
(with P.~Schmidt)
in L.~M\'aty\'as and P.~Sevestre eds.,
{\it The Econometrics of Panel Data\/} vol 1/2,
Dordrecht: Kluwer Academic Publishers (1996).

\medskip

\itemitem{}
``Marriage and Wages''
(with P.~Rupert),
{\it Economic Review\/}, Federal Reserve Bank of Cleveland  4 (1995) 10--20.

\medskip

\itemitem{}
``External Financing, Liquidity and Capital Expenditures:
  Evidence from Panel Data''
(with W.~Beranek and S.~Choi),
{\it Journal of Financial Research\/} 28 (1995) 207--222.

\medskip

\itemitem{}
``Estimating the Economic Model of Crime with Panel Data''
(with W.~Trumbull),
{\it Review of Economics and Statistics\/} (1994) 360--366.
Reprinted in R.~S.~Wassmer, ed.,
{\it Readings in Urban Economics: Issues and Public Policy\/},
Malden, MA: Basil Blackwell (1999).

\medskip

\itemitem{}
``Women and Minorities in Federal Government Agencies:
  Examining New Evidence from Panel Data''
(with E.~Kellough),
{\it Public Administration Review\/} 54 (1994) 265--271.

\medskip

\itemitem{}
``Parametric Estimation of Technical and Allocative
  Inefficiency with Panel Data''
(with S.~Atkinson),
{\it International Economic Review\/} 35 (1994) 231--244.

\medskip

\itemitem{}
``Estimating Output and Input Technical Efficiency Using
  a Flexible Functional Form and Panel Data''
(with S.~Atkinson),
{\it International Economic Review\/} 35 (1994) 245--256.

\medskip

\itemitem{}
``Measuring Technical Efficiency with Panel Data: A Dual Approach''
 (with S.~Atkinson),
{\it Journal of Econometrics\/} 59 (1993) 257--262.

\medskip

\itemitem{}
``Simultaneous Equations and Panel Data''
(with P.~Schmidt and D.~Wyhowski),
{\it Journal of Econometrics\/} 51 (1992) 151--181.

\medskip

\itemitem{}
``Models for which the MLE and the Conditional MLE Coincide''
(with P.~Schmidt),
{\it Empirical Economics\/} 17 (1991) 67--75.

\medskip

\itemitem{}
``Opportunistic Behavior by Firms in Implicit Pension Contracts''
(with S. Dorsey and N.~Mehrzad),
{\it Journal of Human Resources\/} 26 (1991) 704--725.

\medskip

\itemitem{}
``Production Frontiers with Cross-Sectional and Time-Series Variation in
  Efficiency Levels''
(with P.~Schmidt and R.~Sickles),
{\it Journal of Econometrics\/} 46 (1990) 185--200.
Reprinted in G.~S.~Maddala, ed.,
{\it The Econometrics of Panel Data\/}, vol. 2,
Cheltenham: Edward Elger (1993).
{\it Journal of Econometrics\/} ``All-Star Paper'' as defined by citations
over the period 1980-99; 29th most cited.

\medskip

\itemitem{}
``Efficient Estimation with Panel Data:
 An Empirical Comparison of Instrumental Variables Estimators''
(with P.~Rupert),
{\it Journal of Applied Econometrics\/} 3 (1988) 149--155.

\vfil\eject

\item{} {\bf Other Papers}

\bigskip

\itemitem{}
``How Well Does the New SAT Explain First-year College Outcomes by Race and Gender'',
in {\it SAT Wars: The Case for Test-Optional College Admissions\/},
edited by Joseph A. Soares, Columbia University Teacher College Press (2011).

\medskip

\itemitem{}
``Georgia's HOPE Program: An Overview'',
(with E. Bradley and D. Mustard)
in {\it Georgia Education Policy Papers:
A Collection of Policy Papers for the 2009 Legislative Session\/},
Education Policy and Evaluation Center, University of Georgia (2009).

\medskip

\itemitem{}
``Evaluating HOPE-Style Merit Scholarships'',
(with D. Mustard)
in {\it Innovation in Education\/},
Federal Reserve Bank of Cleveland Conference Proceedings (2006).

\medskip

\itemitem{}
``Assessing Public Higher Education in Georgia at the Start of the
21st Century'',
(with D. Mustard)
in {\it What's Happening to Public Higher Education\/},
edited by Ronald Ehrenberg,
Westport CT: Praeger/American Council Series on Higher Education (2006).

\medskip

\itemitem{}
``Georgia's HOPE Scholarship and Minority and Low-Income Students:
Program Effects and Proposed Reforms'',
(with D. Mustard)
in {\it State Merit Scholarship Programs and Racial Inequality\/},
edited by Donald E. Heller and Patricia Marin,
Cambridge MA: The Civil Rights Project, Harvard University (2004).

\medskip

\itemitem{}
``Georgia's HOPE Scholarship Program: Enrollment Gains and Lottery Finance''
(with D. Mustard),
{\it Insights on Southern Poverty\/} vol 1, no 3 (2003).

\medskip

\itemitem{}
``Race and the Effects of Georgia’s HOPE Scholarship''
(with D. Mustard),
in {\it Who Should We Help? The Negative Social Consequences of Merit Scholarships\/},
edited by Donald E. Heller and Patricia Marin,
Cambridge, MA: The Civil Rights Project, Harvard University (2002).

\medskip

\itemitem{}
``HOPE, the Brain Drain, and Diversity:
  The Impact of the Scholarship on High Achievers and African Americans'',
{\it Policy Notes\/}, vol 3, no 4,
Carl Vinson Institute of Government, University of Georgia, 2002.

\medskip

\itemitem{}
``HOPE Affects Where, Not Whether, Students Attend College''
(with D. Mustard),
{\it Policy Notes\/}, vol 2, no 10,
Carl Vinson Institute of Government, University of Georgia, 2001.

\medskip

\itemitem{}
``A Longitudinal Analysis of Individual Changes in Private
  Pension Coverage''
(with S. Dorsey), in
{\it Pension Coverage Issues for the 90s\/},
US Department of Labor, 1994.

\bigskip

\item{} {\bf Book Reviews}

\bigskip

\itemitem{}
{\it Introductory Econometric Theory\/} by Paul A. Ruud,
Oxford University Press, Oxford UK (2000),
{\it Southern Economic Journal\/} 67 (2001) 1025--1028.

\bigskip

\noindent {\bf WORKING PAPERS}

\medskip

\itemitem{}
``Policy or Perception? Women's Political Liberalization and Sex Selection in India''
(with N. Biswas and L. Zimmermann).

\itemitem{}
``Estimating Self Harm in a Large Urban County Jail''
(with Scott Cunningham and Jonathan Seward)

\itemitem{}
``Evaluating the Impact of Self Harm Prevention Offices on Inmate Self Harm in a Large State Prison System''
(with Scott Cunningham and Jonathan Seward)

% \medskip
%
% \itemitem{}
% ``Mass Incarceration's Effect on Risky Sex''
% (with S. Cunningham).

\medskip

% \itemitem{}
% ``Racial Classification and the Race-Wage Gap in Brazil: Evidence from Administrative and Survey Data''
% (with J. Rivera and I. Schmutte)

%\itemitem{}
%``Sex Ratios and Risky Sexual Behavior''
%(with S. Cunningham).%, under revision for {\it Journal of Human Resources\/}.
%
%\medskip
%
%\itemitem{}
%``Merit Aid and Sorting: The Effects of HOPE-Style
%  Scholarships on College Stratification by
%  Ability, Race, and Gender''
%(with E. Bradley and D. Mustard).
%
%\medskip
%
%\itemitem{}
%``The Effects of State-Sponsored Merit Scholarships on Course Selection
%  Major Choice in College''
%(with D. Mustard and K. Lee).
%
%\medskip
%
% \itemitem{}
% ``Estimating Student Responses to HOPE Scholarship Retention Rules Using
% Non-Parametric Matching Techniques''
% (with B. Quinif).
%
% \medskip
%
% \itemitem{}
% ``Religious Background and the Labor Supply and Wages of Young Women''
% (with K. Tinsley and R. Warren).
%
% \medskip
%
% \itemitem{}
% ``The Distributional Impacts Lottery-Funded, Merit-Based
%   College Scholarships: Evidence from Georgia''
% (with D. Mustard).
%
% \itemitem{}
% ``Rules, Incentives and Policy Implications of Large-Scale Merit-Based Financial Aid''
% (with D. Mustard and M. Leidner)
%
% \medskip
%
% \itemitem{}
% ``Estimating Marginal Deterrence with Panel Data''
% (with W. Trumbull).
%
% \medskip
%
% \itemitem{}
% ``Productivity Convergence and Economic Growth: A Frontier Production
%   Function Approach''
% (with J. W\"achter).
%
% \medskip
%
% \itemitem{}
% ``Productivity Convergence and Catch-up in the Manufacturing Sector''
% (with J. W\"achter).
%
% \medskip
%
% \itemitem{}
% ``Comovement and Catch-up in Productivity Across Sectors:
%   Evidence from the OECD''
% (with J. W\"achter).


\bigskip

\noindent {\bf PROFESSIONAL ACTIVITIES}

\bigskip

\item{} {\bf Editorial Boards}

\bigskip

\itemitem{} {\it Journal of Productivity Analysis\/}, 2004--2011
\itemitem{} {\it Journal of Real Estate Finance and Economics\/}, 1991--94

\bigskip

\item{} {\bf Referee}

\bigskip

\itemitem{} {\it American Economic Journal: Applied Economics\/}
\itemitem{} {\it Canadian Journal of Economics\/}
\itemitem{} {\it Contemporary Economic Policy\/}
\itemitem{} {\it Econometric Reviews\/}
\itemitem{} {\it Econometric Theory\/}
\itemitem{} {\it Economic Inquiry\/}
\itemitem{} {\it Economic Journal\/}
\itemitem{} {\it Economics Letters\/}
\itemitem{} {\it Economics of Education Review\/}
\itemitem{} {\it Economie et Pr\'evision\/}
\itemitem{} {\it Educational Evaluation and Policy Analysis\/}
\itemitem{} {\it Education Policy\/}
\itemitem{} {\it Education Economics\/}
\itemitem{} {\it Education Finance and Policy\/}
\itemitem{} {\it Empirical Economics\/}
\itemitem{} {\it European Economic Review\/}
\itemitem{} {\it European Journal of Operations Research\/}
\itemitem{} {\it Industrial and Labor Relations Review\/}
\itemitem{} {\it International Economic Review\/}
\itemitem{} {\it Hungarian Statistical Review\/}
\itemitem{} {\it Journal of Applied Econometrics\/}
\itemitem{} {\it Journal of the American Statistical Association\/}
\itemitem{} {\it Journal of Development Economics\/}
\itemitem{} {\it Journal of Econometrics\/}
\itemitem{} {\it Journal of Economics and Management Strategy\/}
\itemitem{} {\it Journal of Empirical Finance\/}
\itemitem{} {\it Journal of Human Resources\/}
\itemitem{} {\it Journal of Labor Economics\/}
\itemitem{} {\it Journal of Policy Analysis and Management\/}
\itemitem{} {\it Journal of Political Economy\/}
\itemitem{} {\it Journal of Productivity Analysis\/}
\itemitem{} {\it Journal of Real Estate Finance and Economics\/}
\itemitem{} {\it Journal of Urban Economics\/}
\itemitem{} {\it Oxford Bulletin of Economics and Statistics\/}
\itemitem{} {\it Public Finance Review\/}
\itemitem{} {\it Quarterly Journal of Economics\/}
\itemitem{} {\it Regional Science and Urban Economics\/}
\itemitem{} {\it Review of Economics and Statistics\/}
\itemitem{} {\it Scandinavian Journal of Economics\/}
\itemitem{} {\it Southern Economic Journal\/}
\itemitem{} {\it Statistica Neerlandica\/}
\itemitem{} {\it The Statistician,
                 Journal of the Royal Statistical Society Series D\/}
\itemitem{} National Science Foundation
\itemitem{} Research Grants Council of Hong Kong
\itemitem{} Social Sciences and Humanities Research Council of Canada

\bigskip

\item{} {\bf PhD Students (primary advisor), initial placement, year completed}

\bigskip

\itemitem{} Nabaneeta Biswas, Marshall University, 2017
\itemitem{} Jason Rivera, EXL, 2014
\itemitem{} Bing Xu, Southwestern University of Finance and Economics, 2010
\itemitem{} Scott Cunningham, Baylor University, 2007
\itemitem{} Kyung Hee Lee, Sogang University, 2004
\itemitem{} Deepa Sridhar, Rutgers (visiting), 2001
\itemitem{} Jens W\"achter, ZEI Research Center for European Integration, 1998

\bye

\noindent {\bf REFERENCES}

\bigskip

\itemitem{} Available on request.

\bye

\bigskip

\item{} {\bf Contributed Conference Presentations}

\bigskip

\itemitem{}
Southern Economics Association Meetings,
Washington DC, 2018

\medskip

\itemitem{}
Econometric Society European Meetings,
Lisbon Portgual, 2017

\medskip

\itemitem{}
ASSA Meetings,
Chicago IL, 2017

\medskip

\itemitem{}
Econometric Society World Congress,
Montreal Canada, August 2015

\medskip

\itemitem{}
Econometric Society Meetings,
Boston MA, January 2015

\medskip

\itemitem{}
Southern Economic Association Meetings,
Atlanta GA, November 2014

\medskip

\itemitem{}
Latin American Econometric Society Meetings,
Sao Paulo, Brazil, November 2014

\medskip

\itemitem{}
Econometric Society European Meetings,
Gothenberg, Sweden, August 2013

\medskip

\itemitem{}
Econometric Society European Meetings,
Oslo, Norway, August 2011

\medskip

\itemitem{}
Association for Education Finance and Policy Meeting,
Seattle, WA, March 2011

\medskip

\itemitem{}
Joint meetings of the European Association of Labor Economists and the Society of Labor Economists,
London, UK, June 2010

\medskip

\itemitem{}
American Economic Association Meetings,
Atlanta, GA, January 2010

\medskip

\itemitem{}
Society of Labor Economists Meetings,
New York NY, May 2008

\medskip

\itemitem{}
Allied Social Science Association Meetings,
New Orleans LA, January 2008

\medskip

\itemitem{}
European Econometric Society Meetings,
Budapest, August 2007

\medskip

\itemitem{}
Population of Association of America Meetings,
New York NY, March 2007

\medskip

\itemitem{}
Latin American Econometric Society Meetings,
Mexico City, November 2006

\medskip

\itemitem{}
13th Panel Data Conference,
Cambridge UK, July 2006

\medskip

\itemitem{}
American Education Finance Association Meeting,
Louisville KY, March 2005

\medskip

\itemitem{}
Southern Economic Association Meetings,
New Orleans LA, November 2004

\medskip

\itemitem{}
European Economics Association Meetings,
Madrid, Spain, August 2004

\medskip

\itemitem{}
Eleventh Conference on Panel Data,
College Station TX, June 2004

\medskip

\itemitem{}
American Education Finance Association Meeting,
Salt Lake City UT, March 2004

\medskip

\itemitem{}
NBER Higher Education Meeting,
Cambridge MA, November 2003

\medskip

\itemitem{}
European Economic Association Meetings,
Stockholm Sweden, August 2003

\medskip

\itemitem{}
European Society for Population Economics,
New York NY, June 2003

\medskip

\itemitem{}
American Economic Association Meetings,
Washington DC, January 2003

\medskip

\itemitem{}
Southern Economic Association,
New Orleans LA, November 2002

\medskip

\itemitem{}
Society of Labor Economists Meetings,
Baltimore MD, May 2002

\medskip

\itemitem{}
European Economics Association Meetings,
Lausanne, Switzerland, August/September 2001

\medskip

\itemitem{}
Society of Labor Economists Meetings,
Austin TX, April 2001

\medskip

\itemitem{}
Society of Government Economists Meetings,
New Orleans LA, January 2001

\medskip

\itemitem{}
NBER Higher Education Meeting,
Cambridge MA, November 2000

\medskip

\itemitem{}
Southern Economic Association Meetings,
Washington DC, November 2000

\medskip

\itemitem{}
Econometric Society European Meetings,
Santiago de Compostela, Spain, August/September 1999

\medskip

\itemitem{}
German Labor Market Problems: An Empirical Assessment,
Humboldt University, Berlin, Germany, August 1998

\medskip

\itemitem{}
Econometric Society European Meetings,
Toulouse, France, August 1997

\medskip

\itemitem{}
Taipei International Conference on Efficiency and Productivity,
Taipei, Taiwan, June 1997

\medskip

\itemitem{}
% ``Measuring Productivity Change Using a Malmquist Index: Stochastic
%   Distance Function Estimation vs DEA''
Georgia Productivity Conference, Athens, GA, November 1996

\medskip

\itemitem{}
%``Parametric Panel Data Approaches to Estimating
% Price and Technical Inefficiency at the Firm Level'',
Econometric Society World Congress, Tokyo, Japan, August 1995

\medskip

\itemitem{}
% ``Estimating Productivity Growth Using Distance and
% Non-Distance Measures'',
Georgia Productivity Conference, Athens, GA, October 1994

\medskip

\itemitem{}
%``Parametric Testing of Technical Efficiency and
% Profit Maximization with Panel Data'',
Econometric Society European Meetings, Maastricht, The Netherlands,
August 1994

\medskip

\itemitem{}
%``Parametric Testing of Technical Efficiency and
% Profit Maximization with Panel Data'',
Fifth Conference on Panel Data, Paris, France, June 1994.

\medskip

\itemitem{}
% ``Estimating Output and Input Technical Efficiency Using
% a Flexible Functional Form and Panel Data: A Profit Function
% Approach'',
Econometric Society Winter Meetings, Boston, MA, January 1994.

\medskip

\itemitem{}
% ``Parametric Estimation of Technical and Allocative
% Inefficiency With Panel Data'',
Econometric Society European Meetings, Uppsala, Sweden, August 1993

%\vfil\eject
\bigskip

%----------------------Insert Invited Presentations-------------------------

%\input invited.tex

%\bigskip

%-----------------------Insert Discussant Events----------------------------

% \bigskip
%
% \input discuss.tex
